The effects of COVID-19 related social media use on well-being

### 2022-11-17 manuscript.Rmd
- small changes likely bc different mac was used.

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
# output            :
#   papaja::apa6_pdf:
#     latex_engine  : xelatex
# output            : papaja::apa6_docx
output            : html_document
---

>>>>

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            :
  papaja::apa6_pdf:
    latex_engine  : xelatex
# output            : papaja::apa6_docx
# output            : html_document
---
